The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-07-17 ms.tex
Final changes before first submission
Edits from Michael and Beto comments

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{tere-figs/Figure2a}
  \caption{Top panel shows the slit positions from the 2015 run, these are indicated as solid lines and 
labeled at the top against an [O III] HST image. Dashed lines refer to additional slit positions from other runs
and are labeled at the bottom of the image. The middle and bottom panels show the slit positions from 
the other runs placed at different position angles. }
  \label{fig:slit-positions}
\end{figure}

@@

All data was reduced using standard IRAF\footnote{IRAF is
  distributed by the National Optical Astronomy Observatory, which is
  operated by the Association of Universities for Research in
  Astronomy, Inc. under cooperative agreement with the National
  Science foundation} routines.
Bias and cosmic-ray removal was followed by rectification and first-order wavelength 
calibration of the two-dimensional spectra
based on the comparison spectrum
of a Th/Ar lamp, yielding an accuracy in velocity units of \SI{\pm 1}{km.s^{-1}}.
Figure~\ref{fig:pv-array} shows example position-velocity arrays of (left-to-right)
\Ha{} \Wav{6563}, \nii{} \Wav{6583}, and \oiii{} \Wav{5007} for the 11 individual positions from the 2015 run.
The velocity scale is heliocentric 
and the scale along the slit is specified as arcsecond offsets from the central star.
% We derive a heliocentric
% systemic velocity, \(\vsys = \SI{40}{km.s^{-1}}\) by using the slit position F (epoch 2003) that passes through the central star and is not saturated. 
An additional slit (X, shown in Figure~\ref{fig:halo-knots}) was placed on the northern outskirts of the nebula 
in the outer halo of NGC~6210 where filaments had been clearly detected in some of our deep images.\footnote{For this spectrum only, \(3 \times 3\) pixel on-chip binning was used.}
% The observation was carried out on 18 September 2019.  The spectrum was obtained in order 87 (\Ha{} and \nii lines) with the 150 micron slit oriented at a position angle of 56 degrees.  The detector was again the Marconi 2048x2048 with a 3$\times$3 binning.  The spectral dispersion was 0.087 \AA/pix and 0.525\arcsec/pixel.
Most of the spectra presented here are publicly available from the \mbox{San Pedro Mártir} Kinematic Catalogue of Galactic Planetary Nebulae\footnote{
  \url{http://kincatpn.astrosen.unam.mx}
}
\citep{Lopez:2012a}.

@@

From the lower panel of Figure~\ref{fig:knot-complex-velocity-axes},
it is apparent that there is a significant gradient of \(\approx \SI{20}{km.s^{-1}}\)
along axis~B, which is seen in both blue-shifted and red-shifted components.
The sense of this gradient is the same as that seen in the high-ionization shells
along this axis.
It is mainly due to velocity differences
\emph{between} complexes rather than within them,
although both the SW Red and NE Blue complexes
show significant internal gradients of \(\approx \SI{10}{km.s^{-1}}\) in the same direction.
There is an approximate kinematic and spatial symmetry
between pairs of opposite knot complexes:
SW Red with NE Blue, NW Red with SE Blue,
and NE Red with SE Faint Blue.
% It is possible that the west and east sides of the N Red complex
% are actually two separate complexes,
% in which case the east side would pair with the SW Faint Blue complex,
% which would further reinforce this symmetry.

@@

For each of the nebular features listed in Table~\ref{tab:3d},
we have measured the \Ha{} surface brightness \(S(\Ha)\) and flux \(F(\Ha) = S(\Ha)\,d\Omega\),
where \(d\Omega\) is the solid angle of each feature.
Results aggregated by type of feature are presented in Table~\ref{tab:summary}.
Column~2 gives the fraction of the total \Ha{} flux due to each component,
which is dominated by roughly equal contributions from the high-ionization inner shell and the low-ionization knot complexes, summing to over 85\% of the total.

@@

The innermost nebular components of NGC~6210 are the nested high ionization shells:
the inner shell, with a radius of about \SI{0.05}{pc}
and the intermediate shell, with a radius of about \SI{0.1}{pc}.
The intermediate shell is the more massive (Table~\ref{tab:summary})
but the inner shell is roughly 5 times denser and dominates the emission line flux from the nebula.
In terms of the GISW model, the intermediate shell represents the detached stellar envelope
that was ejected during a short period of intense mass loss at the end of the AGB phase,
while the inner shell represents material at the inner edge of the detached envelope
that has been compressed by a shock driven by the fast stellar wind from the central stellar remnant.\footnote{%
  Various different names for these components appear in the literature.
  \citet{Villaver:2002a} use ``intermediate shell'' in the same sense that we do
  and use ``main shell'' for the inner shell when it dominates the brightness.
  On the other hand, \citet{Balick:2002a} prefer ``mantle'' and ``rim'',
  while Schönberner and collaborators consistently use ``shell'' for the outer structure
  and ``rim'' for the inner structure
  \citep[e.g.,][]{Perinotto:2004a, Schonberner:2014a, Schonberner:2018a}.
}
The expansion velocity of the inner shell (\num{30} to \SI{50}{km.s^{-1}})
is higher than that of the intermediate shell (\num{20} to \SI{30}{km.s^{-1}}),
which is the opposite to the trend that is typically seen in multiple-shell planetary nebulae \citep{Corradi:2007a}.
In a sample of 20 high-luminosity nebulae, \citet{Schonberner:2014a} find that the intermediate shell expansion velocity lies in the range \num{20} to \SI{40}{km.s^{-1}},
while the inner shell velocity is always slower at \num{10} to \SI{30}{km.s^{-1}}.
On the other hand, a faster inner shell such as the Turtle's
is not totally unprecedented,
with a particularly extreme example being NGC~2392,
where the inner shell has an observed expansion velocity of up to \SI{120}{km.s^{-1}} \citep{Garcia-Diaz:2012a}.
In both nebulae the inner shell is non-spherical,
with fastest expansion along the line of sight in NGC~2392,
but in the plane of the sky in the case of the Turtle.
In addition, the Turtle's inner shell is not cylindrically symmetric but rather shows two distinct axes, A and B (\S~\ref{sec:high-ioniz-shells}).
Axis~A corresponds to the projected major axis of the inner shell,
which lies close to the plane of the sky,
while axis~B is inclined at roughly \ang{40} to the plane of the sky
and corresponds to the largest net velocity gradient across the shell.
Axis~B also coincides with the major axis of the intermediate shell,
which seems to have a simpler, more elliptical morphology,
albeit slightly lop-sided.

@@

\citet{Guerrero:2020a} studied the kinematics of jets in a sample of 58 planetary nebulae.
They found that the observed distribution of radial velocities can be reproduced by a bimodal distribution of three-dimensional space velocities: 
70\% of nebulae have low-velocity jets with \(V = \SI{66 \pm 26}{km.s^{-1}}\),
while 30\% have high-velocity jets with \(V = \SI{180 \pm 60}{km.s^{-1}}\).
All of the collimated outflows that we find in the Turtle,
with \(V = \num{30}\) to \SI{90}{km.s^{-1}}, are typical of the low-velocity jet population.

@@

\subsubsection{Asymmetries}
\label{sec:asymmetries}
One of the most obvious qualities of the Turtle Nebula is its chaotic and unstructured appearance,
far from the neat symmetries of many other planetary nebulae.
In part this is due to the shear number of symmetry axes in the nebula
(we have found at least five of them),
but there are also asymmetries \emph{along} many of the axes.
In this section we collect together the principle ways in which the nebula is lop-sided:
\begin{enumerate}[1.]
\item The inner shell emission in \oiii{} and \Ha{} shows brightness asymmetries in both position and velocity.
  The redshifted half of the shell is roughly twice as bright as the blueshifted half,
  while both halves show spatial asymmetries along axis~A, but in opposite senses:
  redshifted emission is 2.5 times brighter on the north side,
  while blueshifted emission is 1.5 times brighter on the south side.
  Because the inner shell dominates the total flux, this leads to a north--south asymmetry in the nebula as a whole,
  with the peak brightness region lying 2~arcsec north of the central star. 
\item In the \heii{} line, the inner shell has an opposite asymmetry: it is brighter to the south than to the north.
  Such an asymmetry is hard to explain if the \chem{He^{2+}} zone of the nebula is ionization-bounded and the central star emits isotropically.
\item The intermediate shell shows an egg-shaped morphology that is lop-sided along its major axis (axis~B),
  extending roughly 30\% further from the star to the WSW than to the ENE.\@ 
\item The outer lobes are probably the \emph{least} asymmetric component of the entire nebula,
  consisting as they do of balanced point-symmetric red-blue pairs of emission components along the axes A, C, and D (Figure~\ref{fig:outer-lobe-systems}).
  However, there is one significant asymmetry: \oiii{} system \SysP{7},
  which corresponds to the N~knot in \nii{} has no corresponding blue-shifted feature to the S.
\item With the low-ionization knot complexes,
  the principle asymmetry is between the redshifted and blueshifted knots.
  The redshifted knots are brighter by a factor of 2.5,
  slower-moving by a factor of 1.5,
  and further from the star by a factor of 2.
\item In the halo, the only significant asymmetry is in the halo knots,
  which are found only to the N and E of the star. 
\end{enumerate}

What is the origin of the asymmetries?
Mechanisms proposed to date \citep{Soker:2004b, Soker:2016b}
involve accretion disk and jet formation in a triple star system.
This may be via accretion of the AGB wind onto a close binary on a wide orbit around the AGB,
or, if the orbit is closer, via a common envelope or grazing envelope phase,
which may or may not result in the merger of the close binary pair.
The descendant system would be binary if a merger or ejection occurred,
or still a triple if not,
but there is no direct evidence that the Turtle's central star is binary or triple.
The fact that the basic parameters of the nebula and its central star can be consistently interpreted in terms of single-star evolution (see \S~\ref{sec:comparison-with-post})
suggests that a triple interaction was not required for the initial ejection of the envelope that forms the intermediate shell,
although it may be responsible for its subsequent shaping.

@@

We also select a secondary sample of Peimbert Type~IIb,
which otherwise meet the 5 criteria given above,
yielding another six sources:
NGC~6891 (\G{054.1}{-12.1}), 
NGC~6892 (\G{009.4}{-05.0}), 
 IC~2448  (\G{285.7}{-14.9}), 
NGC~3242 (\G{261.0}{+32.0}), 
NGC~6826 (\G{083.5}{+12.7}),
and NGC~6309 (\G{009.6}{+14.8}).\footnote{
  We relax criterion 5 to admit NGC~6309, which has spectral classification ``O(He)?''.  
}
Applying the same criteria to Type~IIa nebulae yields more than 10 sources,
from which we cherry pick five of the most famous:
NGC~6578 (\G{010.8}{-01.8}), 
NGC~2392 (\G{197.0}{+17.3}), 
NGC~7009 (\G{037.7}{-34.5}), 
NGC~5882 (\G{327.8}{+10.0}), 
and NGC~6543 (\G{096.4}{+29.9}).\footnote{
  Again, we relax criterion 5 to admit NGC~6543, which has spectral classification ``Of-WR(H)''.
  We also relax criterion 4 to admit NGC~2392, which is slightly larger than the other nebulae (\(R = \SI{0.22}{pc}\)).
} 
Type~II nebulae 
have low \(z\)-heights and peculiar velocities,
indicating membership of a younger, thin-disk stellar population \citep{Quireza:2007a}.
Type~IIb have similar abundances to Type~III,
while type~IIa are moderately enriched in N and He. 
On average, the progenitor mass should increase in sequence from Type~III,
through IIb, to IIa,
but there is a large overlap between the types \citep{Stanghellini:2018a}
and by filtering on both \teff{} and \(R\) we are probably restricting our samples to a narrow range of masses.%
\footnote{
  The highest mass progenitors (\(M > \SI{2}{\msun}\)) are associated with Peimbert Type~I nebulae,
  but no such nebulae from the \citet{Quireza:2007a} catalog satisfy our combined constraints.
  This may well be because the faster evolutionary timescale of higher mass stars on the post-AGB heating track
  (see \S~\ref{sec:comparison-with-post})
  means that \teff{} exceeds \SI{100}{kK} while the nebula is still compact,
  \(R < \SI{0.07}{pc}\).
}

>>>>

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{tere-figs/Figure2a}
   \caption{
     Spectrograph slit positions for vertical orientations (upper panel),
     horizontal orientations (middle panel),
     and diagonal orientations (lower panel).
     Background image in each case is an \textit{HST} \oiii{} image of the nebula.
     In the top panel, slit positions from the 2015 season are indicated as solid lines
     and positions from other seasons are shown as dashed lines (see Table~\ref{table:pa5} for details). 
   }
  \label{fig:slit-positions}
\end{figure}

@@

All data was reduced using standard IRAF\footnote{IRAF was originally
  distributed by the National Optical Astronomy Observatory,
  \url{http://ast.noao.edu/data/software},
  and is currently available from \url{https://iraf-community.github.io}.}
routines.
Bias and cosmic-ray removal was followed by rectification and first-order wavelength 
calibration of the two-dimensional spectra
based on the comparison spectrum
of a Th/Ar lamp, yielding an accuracy in velocity units of \SI{\pm 1}{km.s^{-1}}.
Figure~\ref{fig:pv-array} shows example position-velocity arrays of (left-to-right)
\Ha{} \Wav{6563}, \oiii{} \Wav{5007}, and \nii{} \Wav{6583} for the 11 individual positions from the 2015 run.
The velocity scale is heliocentric 
and the scale along the slit is specified as arcsecond offsets from the central star.
% We derive a heliocentric
% systemic velocity, \(\vsys = \SI{40}{km.s^{-1}}\) by using the slit position F (epoch 2003) that passes through the central star and is not saturated. 
An additional slit (X, shown in Figure~\ref{fig:halo-knots}) was placed on the northern outskirts of the nebula 
in the outer halo of NGC~6210 where filaments had been clearly detected in some of our deep images.\footnote{For this spectrum only, \(3 \times 3\) pixel on-chip binning was used.}
% The observation was carried out on 18 September 2019.  The spectrum was obtained in order 87 (\Ha{} and \nii lines) with the 150 micron slit oriented at a position angle of 56 degrees.  The detector was again the Marconi 2048x2048 with a 3$\times$3 binning.  The spectral dispersion was 0.087 \AA/pix and 0.525\arcsec/pixel.
Most of the spectra presented here are publicly available from the \mbox{San Pedro Mártir} Kinematic Catalogue of Galactic Planetary Nebulae\footnote{
  \url{http://kincatpn.astrosen.unam.mx}
}
\citep{Lopez:2012a}.

@@

From the lower panel of Figure~\ref{fig:knot-complex-velocity-axes},
it is apparent that there is a significant gradient of \(\approx \SI{20}{km.s^{-1}}\)
along axis~B, which is seen in both blue-shifted and red-shifted components.
The sense of this gradient is the same as that seen in the high-ionization shells
along this axis.
It is mainly due to velocity differences
\emph{between} complexes rather than within them,
although both the SW Red and NE Blue complexes
show significant internal gradients of \(\approx \SI{10}{km.s^{-1}}\) in the same direction.
There is an approximate kinematic and spatial symmetry
between pairs of opposite knot complexes:
SW Red with NE Blue, NW Red with SE Blue,
and NE Red with SW Faint Blue.
% It is possible that the west and east sides of the N Red complex
% are actually two separate complexes,
% in which case the east side would pair with the SW Faint Blue complex,
% which would further reinforce this symmetry.

@@

For each of the nebular features listed in Table~\ref{tab:3d},
we have measured the \Ha{} surface brightness \(S(\Ha)\) and flux \(F(\Ha) = S(\Ha)\,d\Omega\),
where \(d\Omega\) is the solid angle of each feature.
Results aggregated by type of feature are presented in Table~\ref{tab:summary}.
Column~2 gives the fraction of the total \Ha{} flux due to each component,
which is dominated by the high-ionization inner shell.

@@

The innermost nebular components of NGC~6210 are the nested high ionization shells:
the inner shell, with a radius of about \SI{0.05}{pc}
and the intermediate shell, with a radius of about \SI{0.1}{pc}.
The intermediate shell is the more massive (Table~\ref{tab:summary})
but the inner shell is roughly 5 times denser and dominates the emission line flux from the nebula.
In terms of the GISW model, the intermediate shell represents the detached stellar envelope
that was ejected during a short period of intense mass loss at the end of the AGB phase,
while the inner shell represents material at the inner edge of the detached envelope
that has been compressed by a shock driven by the fast stellar wind from the central stellar remnant.\footnote{%
  Various different names for these components appear in the literature.
  \citet{Villaver:2002a} use ``intermediate shell'' in the same sense that we do
  and use ``main shell'' for the inner shell when it dominates the brightness.
  On the other hand, \citet{Balick:2002a} prefer ``mantle'' and ``rim'',
  while Schönberner and collaborators consistently use ``shell'' for the outer structure
  and ``rim'' for the inner structure
  \citep[e.g.,][]{Perinotto:2004a, Schonberner:2014a, Schonberner:2018a}.
}
The expansion velocity of the inner shell (\num{30} to \SI{50}{km.s^{-1}})
is higher than that of the intermediate shell (\num{20} to \SI{30}{km.s^{-1}}),
which is the opposite to the trend that is typically seen in multiple-shell planetary nebulae \citep{Corradi:2007a}.
In a sample of 20 high-luminosity nebulae, \citet{Schonberner:2014a} find that the intermediate shell expansion velocity lies in the range \num{20} to \SI{40}{km.s^{-1}},
while the inner shell velocity is always slower at \num{10} to \SI{30}{km.s^{-1}}.
In general, the expansion velocities are found to increase with stellar effective temperature
during the high-luminosity phase of central star evolution
\citep{Richer:2008a, Richer:2010a, Pereyra:2016a}.
On the other hand, a faster inner shell such as the Turtle's
is not totally unprecedented,
with a particularly extreme example being NGC~2392,
where the inner shell has an observed expansion velocity of up to \SI{120}{km.s^{-1}} \citep{Garcia-Diaz:2012a}.
In both nebulae the inner shell is non-spherical,
with fastest expansion along the line of sight in NGC~2392,
but in the plane of the sky in the case of the Turtle.
In addition, the Turtle's inner shell is not cylindrically symmetric but rather shows two distinct axes, A and B (\S~\ref{sec:high-ioniz-shells}).
Axis~A corresponds to the projected major axis of the inner shell,
which lies close to the plane of the sky,
while axis~B is inclined at roughly \ang{40} to the plane of the sky
and corresponds to the largest net velocity gradient across the shell.
Axis~B also coincides with the major axis of the intermediate shell,
which seems to have a simpler, more elliptical morphology,
albeit slightly lop-sided.

@@

\citet{Guerrero:2020a} studied the kinematics of jets in a sample of 58 planetary nebulae.
They found that the observed distribution of radial velocities can be reproduced by a bimodal distribution of three-dimensional space velocities: 
70\% of nebulae have low-velocity jets with \(V = \SI{66 \pm 26}{km.s^{-1}}\),
while 30\% have high-velocity jets with \(V = \SI{180 \pm 60}{km.s^{-1}}\).
All of the collimated outflows that we find in the Turtle,
with \(V = \num{30}\) to \SI{90}{km.s^{-1}}, are typical of the low-velocity jet population.
When compared with the general taxonomy of collimated outflows seen in planetary nebulae \citep{Lopez:1997a},
the outer lobes are similar to the class of Bipolar Rotating Episodic Jets
\citetext{BRETs, \citealp{Lopez:1993a}}
while the knot complexes are similar to the class of
Fast Low-Ionization Emission Regions \citetext{FLIERs, \citealp{Balick:1994a}}
with the exception that we find no evidence for enhanced N abundance in the knots,
as is often found in FLIERs.

@@

\subsubsection{Asymmetries}
\label{sec:asymmetries}
One of the most obvious qualities of the Turtle Nebula is its chaotic and unstructured appearance,
far from the neat symmetries of many other planetary nebulae.
In part this is due to the shear number of symmetry axes in the nebula
(we have found at least five of them),
but there are also asymmetries \emph{along} many of the axes.
In this section we collect together the principle ways in which the nebula is lop-sided:
\begin{enumerate}[1.]
\item The inner shell emission in \oiii{} and \Ha{} shows brightness asymmetries in both position and velocity.
  The redshifted half of the shell is roughly twice as bright as the blueshifted half,
  while both halves show spatial asymmetries along axis~A, but in opposite senses:
  redshifted emission is 2.5 times brighter on the north side,
  while blueshifted emission is 1.5 times brighter on the south side.
  Because the inner shell dominates the total flux, this leads to a north--south asymmetry in the nebula as a whole,
  with the peak brightness region lying 2~arcsec north of the central star. 
\item In the \heii{} line, the inner shell has an opposite asymmetry: it is brighter to the south than to the north, as measured in our slit spectra.
  Such an asymmetry is hard to explain if the \chem{He^{2+}} zone of the nebula is ionization-bounded and the central star emits isotropically.
  Note however that there is a gap in our slit coverage in precisely the region of maximum \Ha{} brightness, so it is possible that this discrepancy only apparent.
\item The intermediate shell shows an egg-shaped morphology that is lop-sided along its major axis (axis~B),
  extending roughly 30\% further from the star to the WSW than to the ENE.\@ 
\item The outer lobes are probably the \emph{least} asymmetric component of the entire nebula,
  consisting as they do of balanced point-symmetric red-blue pairs of emission components along the axes A, C, and D (Figure~\ref{fig:outer-lobe-systems}).
  However, there is one significant asymmetry: \oiii{} system \SysP{7},
  which corresponds to the N~knot in \nii{} has no corresponding blue-shifted feature to the S.
\item With the low-ionization knot complexes,
  the principle asymmetry is between the redshifted and blueshifted knots.
  The redshifted knots are brighter by a factor of 2.5,
  slower-moving by a factor of 1.5,
  and further from the star by a factor of 2.
\item In the halo, the only significant asymmetry is in the halo knots,
  which are found only to the N and E of the star. 
\end{enumerate}

What is the origin of the asymmetries?
Mechanisms proposed to date \citep{Soker:2004b, Soker:2016b}
involve accretion disk and jet formation in a triple star system.
This may be via accretion of the AGB wind onto a close binary on a wide orbit around the AGB,
or, if the orbit is closer, via a common envelope or grazing envelope phase,
which may or may not result in the merger of the close binary pair.
The descendant system would be binary if a merger or ejection occurred,
or still a triple if not,
but there is no direct evidence that the Turtle's central star is binary or triple.
The fact that the basic parameters of the nebula and its central star can be consistently interpreted in terms of single-star evolution (see \S~\ref{sec:comparison-with-post})
suggests that a triple interaction was not required for the initial ejection of the envelope that forms the intermediate shell,
although it may be responsible for its subsequent shaping.
The possible role of magnetic fields in shaping the nebula and its bipolar outflows
\citep{Garcia-Segura:2000a}
is also unclear.

@@

We also select a secondary sample of Peimbert Type~IIb,
which otherwise meet the 5 criteria given above,
yielding another seven sources:
NGC~6891 (\G{054.1}{-12.1}),
NGC~6629 (\G{009.4}{-05.0}),
IC~2448 (\G{285.7}{-14.9}), 
NGC~3242 (\G{261.0}{+32.0}), 
NGC~6826 (\G{083.5}{+12.7}),
and NGC~6309 (\G{009.6}{+14.8}),\footnote{
  We relax criterion 5 to admit NGC~6309, which has spectral classification ``O(He)?''.  
}
and IC~4634 (\G{000.3}{+12.2}).
Applying the same criteria to Type~IIa nebulae yields more than 10 sources,
from which we cherry pick five of the most famous:
NGC~6578 (\G{010.8}{-01.8}), 
NGC~2392 (\G{197.0}{+17.3}), 
NGC~7009 (\G{037.7}{-34.5}), 
NGC~5882 (\G{327.8}{+10.0}), 
and NGC~6543 (\G{096.4}{+29.9}).\footnote{
  Again, we relax criterion 5 to admit NGC~6543, which has spectral classification ``Of-WR(H)''.
  We also relax criterion 4 to admit NGC~2392, which is slightly larger than the other nebulae (\(R = \SI{0.22}{pc}\)).
} 
Type~II nebulae 
have low \(z\)-heights and peculiar velocities,
indicating membership of a younger, thin-disk stellar population \citep{Quireza:2007a}.
Type~IIb have similar abundances to Type~III,
while type~IIa are moderately enriched in N and He. 
On average, the progenitor mass should increase in sequence from Type~III,
through IIb, to IIa,
but there is a large overlap between the types \citep{Stanghellini:2018a}
and by filtering on both \teff{} and \(R\) we are probably restricting our samples to a narrow range of masses.%
\footnote{
  The highest mass progenitors (\(M > \SI{2}{\msun}\)) are associated with Peimbert Type~I nebulae,
  but no such nebulae from the \citet{Quireza:2007a} catalog satisfy our combined constraints.
  This may well be because the faster evolutionary timescale of higher mass stars on the post-AGB heating track
  (see \S~\ref{sec:comparison-with-post})
  means that \teff{} exceeds \SI{100}{kK} while the nebula is still compact,
  \(R < \SI{0.07}{pc}\).
}
